An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-03 poly-embed-journal/poly-embed-journal.tex
pass over intro and sec 2... not done in 2 yet

\documentclass[12pt]{article}
\PassOptionsToPackage{numbers, compress, sort}{natbib}
\usepackage[final]{neurips_2019}

@@

\title{An Embedding Framework for Consistent Polyhedral Surrogates}
%\title{Consistent Polyhedral Surrogates via Embeddings}
%\title{Convex Surrogates via Polyhedral Losses}
\author{%
 Jessie Finocchiaro \\
 \texttt{jefi8453@colorado.edu}\\
 CU Boulder
 \And
 Rafael Frongillo\\
 \texttt{raf@colorado.edu}\\
 CU Boulder
 \And
 Bo Waggoner\\
 \texttt{bwag@colorado.edu}\\
 CU Boulder
}

@@

\begin{abstract}
We formalize and study the natural approach of designing convex surrogate loss functions via embeddings for problems such as classification, ranking, or structured prediction. 
In this approach, one embeds each of the finitely many predictions (e.g. classes) as a point in $\reals^d$, assigns the original loss values to these points, and ``convexifies'' the loss in some way to obtain a surrogate.
We prove that this approach is equivalent, in a strong sense, to working with polyhedral (piecewise linear convex) losses.
Moreover, given any polyhedral loss $L$, we give a construction of a link function through which $L$ is a consistent surrogate for the loss it embeds.
We go on to illustrate the power of this embedding framework with succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature.
\end{abstract}

@@

\raf{Old version:} Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (piecewise-linear convex) loss functions.
In particular, by focusing on Bayes risks, we show that every discrete loss is embedded by some polyhedral loss, and every polyhedral loss function embeds some discrete loss.
Moreover, we show that any polyhedral loss gives rise to a calibrated link function to the loss it embeds,
thus giving a very general framework to construct consistent convex surrogates for arbitrary losses.

\raf{New version starting here:}

@@

Moreover, given an existing polyhedral surrogate, we provide tools to find the discrete loss it embeds (Corollary~\ref{cor:representative-embeds-restriction}).
In short, if one can identify a finite \emph{representative set} $\Sc$ of reports for a surrogate $L$, meaning $\Sc$ always contains an $L$-optimal report for any label distribution, then $L$ embeds $L|_\Sc$, the loss given by $L$ restricting to $\Sc$.
We apply these tools to several polyhedral surrogates which have been proposed recently (\S~\ref{sec:applications}), showing that they are inconsistent for the desired target, but are consistent for a different target: the one embedded by the loss.

Underpinning our results are several observations which formalize the idea that polyhedral losses ``behave like'' discrete losses.
For example, discrete losses have polyhedral Bayes risks (as the minimum of finitely many linear functions), and so do polyhedral losses (Lemma~\ref{lem:poly-loss-poly-risk}).
As a consequence, polyhedral losses always have finite representative sets.
Aside from observations like these which we use to prove our main results, we provide several others through the lens of property elicitation which we view as conceptual contributions (\S~\ref{sec:min-rep-sets}).
These latter observations culminate in the following result: when restricting to the class of polyhedral surrogates, indirect elicitation is both necessary and sufficient for consistency (Theorem~\ref{thm:poly-ie-implies-consistent} in \S~\ref{sec:poly-ie-consistency}).

@@

\section{Setting and Main Results}
\label{sec:setting}

@@

Several consistent convex surrogates in the literature can be thought of as \emph{embeddings}, wherein one maps the discrete reports to a vector space, and finds a convex loss which agrees with the original loss.
To allow for ``redundant'' reports, in both the target and surrogate, we first introduce the notions of representative sets; see Proposition~\ref{prop:tfae-min-rep-nonredundant} for a formal connection.
\begin{definition}
  Let $L:\R\to\reals^\Y_+$ be a generic loss.
  We say $\Sc \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
  We further say $\Sc$ is a \emph{minimum representative set} if it has the smallest cardinality among all representative sets.
\end{definition}
\raft{Maybe discussion about minimum representative sets and \emph{maximally informative sets} from~\citet{wang2020weston} here, though maybe best to leave it until later.  BTW, I think their latest version might use different terminology.}

We now formally introduce the concept of an embedding.
In addition to matching loss values, a key condition for consistency is that the original reports should be optimal exactly when the corresponding embedded points are optimal.
\begin{definition}[Embedding a loss]\label{def:loss-embed}
  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ over a representative set $\Sc$ if there exists some injective embedding $\varphi:\Sc\to\reals^d$ such that
  (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\Sc$ we have
  % \begin{equation}\label{eq:embed-loss}
  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
  % \end{equation}
  \begin{equation}\label{eq:embed-loss}
    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
  \end{equation}
  We simply say $L$ \emph{embeds} $\ell$ if there is some representative set $\Sc$ for $\ell$ such that $L$ embeds $\ell$ over $\Sc$.
\end{definition}

>>>>

\documentclass[11pt]{article}
\usepackage[numbers, compress, sort]{natbib}
\usepackage[margin=1.1in]{geometry}

@@

\title{An Embedding Framework for Consistent Polyhedral Surrogates}
%\title{Consistent Polyhedral Surrogates via Embeddings}
%\title{Convex Surrogates via Polyhedral Losses}
\author{%
 Jessie Finocchiaro \\
 \texttt{jefi8453@colorado.edu}\\
 CU Boulder
 \and
 Rafael Frongillo\\
 \texttt{raf@colorado.edu}\\
 CU Boulder
 \and
 Bo Waggoner\\
 \texttt{bwag@colorado.edu}\\
 CU Boulder
}

@@

\begin{abstract}
We formalize and study the natural approach of designing convex surrogate loss functions via embeddings for problems such as classification, ranking, or structured prediction. 
In this approach, one embeds each of the finitely many predictions (e.g. classes) as a point in $\reals^d$, assigns the original loss values to these points, and ``convexifies'' the loss in some way to obtain a surrogate.
We prove that this approach is equivalent, in a strong sense, to working with polyhedral (piecewise-linear convex) losses.
Moreover, given any polyhedral loss $L$, we give a construction of a link function through which $L$ is a consistent surrogate for the loss it embeds.
Our framework yields succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature, and for further reveals the target problems that inconsistent surrogates are consistent for.
We also show \raf{Newer stuff}
\end{abstract}

@@

\raf{The old intro had just one more paragraph here, now commented out}
% Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (piecewise-linear convex) loss functions.
% In particular, by focusing on Bayes risks, we show that every discrete loss is embedded by some polyhedral loss, and every polyhedral loss function embeds some discrete loss.
% Moreover, we show that any polyhedral loss gives rise to a calibrated link function to the loss it embeds,
% thus giving a very general framework to construct consistent convex surrogates for arbitrary losses.

@@

To better understand existing polyhedral surrogates, we provide tools to find the discrete losses they embed (Corollary~\ref{cor:representative-embeds-restriction}).
In short, if one can identify a finite \emph{representative set} $\Sc$ of reports for a surrogate $L$, meaning $\Sc$ always contains an $L$-optimal report for any label distribution, then $L$ embeds $L|_\Sc$, the loss given by $L$ restricting to $\Sc$.
We apply these tools to several polyhedral surrogates which have been proposed recently (\S~\ref{sec:applications}), showing in some cases that they are inconsistent for the desired target, but are consistent for a different target: the discrete loss they embed.

Underpinning our results are several observations which formalize the idea that polyhedral losses ``behave like'' discrete losses.
For example, discrete losses have polyhedral Bayes risks (as the minimum of finitely many linear functions), and so do polyhedral losses (Lemma~\ref{lem:poly-loss-poly-risk}).
As a consequence, polyhedral losses always have finite representative sets, and restricting the loss to any such set is an embedding.

We also provide several observations beyond what is needed to prove our main results, which we view as conceptual contributions (\S~\ref{sec:min-rep-sets},~\ref{sec:poly-ie-consistency}).
Using tools from property elicitation, we show an equivalence between minumum reprosentative sets and ``non-redundancy'', wherein no report is dominated by another.
We further show that, while the minimum representative set is not always unique, the loss values associated with it are unique, giving rise to a natural ``trim'' operation on losses.
Finally, using our main results, we show the following result: when restricting to the class of polyhedral surrogates, indirect elicitation is both necessary and sufficient for consistency (Theorem~\ref{thm:poly-ie-implies-consistent}).

@@

\section{Setting}
\label{sec:setting}

@@

Several consistent convex surrogates in the literature can be thought of as \emph{embeddings} of the target loss $\ell$, wherein one maps the discrete reports of $\ell$ to a vector space, and finds a convex loss which agrees with the original loss.
It turns out that it will be convenient, especially in applications, to allow $\ell$ to have ``redundant'' reports, e.g., reports that are never optimal or never uniquely optimal.
We first formalize two notions of non-redundancy, and then turn to our formal definition of embeddings.

\raf{Story: Def non-redundant.  Then talk about rep sets.  If it is minimum, that's another way to formalize non-redundant. prove equivalence of these two in BLAH.  Use abstain loss for binary classification as a running example.}
To allow for ``redundant'' reports, in both the target and surrogate, we first introduce the notions of representative sets; see Proposition~\ref{prop:tfae-min-rep-nonredundant} for a formal connection.
\begin{definition}
  Let $L:\R\to\reals^\Y_+$ be a generic loss.
  We say $\Sc \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
  We further say $\Sc$ is a \emph{minimum representative set} if it has the smallest cardinality among all representative sets.
\end{definition}
\raft{Maybe discussion about minimum representative sets and \emph{maximally informative sets} from~\citet{wang2020weston} here, though maybe best to leave it until later.  BTW, I think their latest version might use different terminology.}

\raf{Add ``tight'' to this def now}
We now formally introduce the concept of an embedding.
In addition to matching loss values, a key condition for consistency is that the original reports should be optimal exactly when the corresponding embedded points are optimal.
\begin{definition}[Embedding a loss]\label{def:loss-embed}
  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ over a representative set $\Sc$ if there exists some injective embedding $\varphi:\Sc\to\reals^d$ such that
  (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\Sc$ we have
  % \begin{equation}\label{eq:embed-loss}
  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
  % \end{equation}
  \begin{equation}\label{eq:embed-loss}
    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
  \end{equation}
  We simply say $L$ \emph{embeds} $\ell$ if there is some representative set $\Sc$ for $\ell$ such that $L$ embeds $\ell$ over $\Sc$.
\end{definition}
